---
title: "Jess's Practice Code"
author: "Jess Garcia"
date: "4/18/2021"
output: pdf_document
editor_options: 
  chunk_output_type: console
---
## View & Wrangle data
```{r setup,  warning=FALSE, message=FALSE, include = FALSE}
#install.packages("tseries")

library(tidyverse)
library(trend)
library(zoo)
library(Kendall)
library(tseries)
library(lubridate)
library(cowplot)


Radiance_data_long <- read.csv('../Data/Long_20210419.csv')

#Set date as date, create month & day column then join
class(Radiance_data_long$Year)

Radiance_data_long$Month <- 1
Radiance_data_long$Day <-1

Radiance_data_long <-
  Radiance_data_long %>% 
  mutate(Date=(paste0(Year,"-",Month,"-",Day)))


Radiance_data_long$Date <- as.Date(Radiance_data_long$Date, format= "%Y-%m-%d")


class(Radiance_data_long$Date)


#Filter for Cities/Counties with policy implementation between 2000-2005

Radiance_data_long_filtered <-
  Radiance_data_long %>% 
  filter(Implemented %in% 2000:2005)
```


```{r eval=FALSE, include=FALSE,  warning=FALSE, message=FALSE}

Radiance_long.plot <-
  ggplot(Radiance_data_long, aes (x=Date, y=value, color= County))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  scale_x_date(date_labels="%Y")+
  theme(axis.text.x = element_text(angle=45, hjust=1))

Radiance_long.plot


Radiance_long_filtered.plot <-
  ggplot(Radiance_data_long_filtered, aes (x=Date, y=value, color= County))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  scale_x_date(date_breaks = "2 years", date_labels = "%Y")+
  theme(axis.text.x = element_text(angle=45, hjust=1))

Radiance_long_filtered.plot
```

```{r eval=FALSE, include=FALSE,  warning=FALSE, message=FALSE}
#Isolating each county
AnnaMaria <- Radiance_data_long_filtered %>% 
  filter(County == "Anna Maria Island")


AnnaMaria.plot <-
 ggplot(AnnaMaria, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(data=subset(data, Date < 2003), method='lm',formula=y~x,se=FALSE, color = "red")+
  geom_smooth(data=subset(data, Date >= 2003), method='lm',formula=y~x,se=FALSE, color = "blue")

AnnaMaria.plot


#Faceting
AnnaMaria$Date <- ifelse(Date < 2003, "Before", "After")

AnnaMaria.plot2 <-
 ggplot(AnnaMaria, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)+ 
  facet_grid(value ~ Date)
 

AnnaMaria.plot2

#Splitting data for before and after 2003


AnnaMaria <- Radiance_data_long_filtered %>% 
  filter(County == "Anna Maria Island")

AnnaMaria.plotA <-
 ggplot(AnnaMaria, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2003-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMaria.plotA



AnnaMaria.plotB <-
 ggplot(AnnaMaria, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2003-01-01","2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMaria.plotB

#Plotting them side by side
plot_grid(AnnaMaria.plotA, AnnaMaria.plotB, nrow=1, align='h')

```


```{r eval=FALSE, include=FALSE,  warning=FALSE, message=FALSE}
#Bay County
BayCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Bay County")

BayCounty.plotA <-
 ggplot(BayCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Bay County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2002-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BayCounty.plotA



BayCounty.plotB <-
 ggplot(BayCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y=" ")+
  ggtitle(" ", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2002-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BayCounty.plotB


plot_grid(BayCounty.plotA, BayCounty.plotB, nrow=1, align='h')


#Mexico Beach
MexicoBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Meixco Beach")

MexicoBeach.plotA <-
 ggplot(MexicoBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Mexico Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

MexicoBeach.plotA



MexicoBeach.plotB <-
 ggplot(MexicoBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Mexico Beach", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

MexicoBeach.plotB


plot_grid(MexicoBeach.plotA, MexicoBeach.plotB, nrow=1, align='h')


#Deerfield Beach
DeerfieldBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Deerfield Beach")

DeerfieldBeach.plotA <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Deerfield Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2000-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

DeerfieldBeach.plotA



DeerfieldBeach.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Deerfield Beach", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2000-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

DeerfieldBeach.plotB


plot_grid(DeerfieldBeach.plotA, DeerfieldBeach.plotB, nrow=1, align='h')



#Fort Lauderdale
FortLauderdale <- Radiance_data_long_filtered %>% 
  filter(County == "Fort Lauderdale")

FortLauderdale.plotA <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Fort Lauderdale", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2003-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FortLauderdale.plotA



FortLauderdale.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Fort Lauderdale", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2003-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FortLauderdale.plotB


plot_grid(FortLauderdale.plotA, FortLauderdale.plotB, nrow=1, align='h')



#Hallandale Beach
HallandaleBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Hallandale Beach")

HallandaleBeach.plotA <-
 ggplot(HallandaleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Hallandale Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

HallandaleBeach.plotA



HallandaleBeach.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Hallandale Beach", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

HallandaleBeach.plotB


plot_grid(HallandaleBeach.plotA, HallandaleBeach.plotB, nrow=1, align='h')




#Lauderdale By the Sea
LauderdaleBySea <- Radiance_data_long_filtered %>% 
  filter(County == "Lauderdale By the Sea")

LauderdaleBySea.plotA <-
 ggplot(LauderdaleBySea, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Lauderdale By the Sea", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2002-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

LauderdaleBySea.plotA


LauderdaleBySea.plotB <-
 ggplot(LauderdaleBySea, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Lauderdale By the Sea", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2002-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

LauderdaleBySea.plotB


plot_grid(LauderdaleBySea.plotA, LauderdaleBySea.plotB, nrow=1, align='h')



#Jacksonville Beach
JacksonvilleBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Jacksonville beach")

JacksonvilleBeach.plotA <-
 ggplot(JacksonvilleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Jacksonville Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2000-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

JacksonvilleBeach.plotA



JacksonvilleBeach.plotB <-
 ggplot(JacksonvilleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Jacksonville Beach", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2000-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

JacksonvilleBeach.plotB


plot_grid(JacksonvilleBeach.plotA, JacksonvilleBeach.plotB, nrow=1, align='h')




#Flagler County
FlaglerCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Flagler COunty")

FlaglerCounty.plotA <-
 ggplot(FlaglerCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Flagler County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FlaglerCounty.plotA



FlaglerCounty.plotB <-
 ggplot(FlaglerCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Flagler County", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FlaglerCounty.plotB


plot_grid(FlaglerCounty.plotA, FlaglerCounty.plotB, nrow=1, align='h')



#Gulf County
GulfCounty <- Radiance_data_long_filtered %>% 
  filter(County == "GUlf COunty")

GulfCounty.plotA <-
 ggplot(GulfCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Gulf County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

GulfCounty.plotA



GulfCounty.plotB <-
 ggplot(GulfCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Gulf County", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

GulfCounty.plotB


plot_grid(GulfCounty.plotA, GulfCounty.plotB, nrow=1, align='h')



#Bonita Springs
BonitaSprings <- Radiance_data_long_filtered %>% 
  filter(County == "Bonita SPrings")

BonitaSprings.plotA <-
 ggplot(BonitaSprings, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Bonita Springs", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BonitaSprings.plotA


BonitaSprings.plotB <-
 ggplot(BonitaSprings, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Bonita Springs", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BonitaSprings.plotB


plot_grid(BonitaSprings.plotA, BonitaSprings.plotB, nrow=1, align='h')





#Anna Maria Island
AnnaMariaIsland <- Radiance_data_long_filtered %>% 
  filter(County == "Anna Maria Island")

AnnaMariaIsland.plotA <-
 ggplot(AnnaMariaIsland, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2003-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMariaIsland.plotA


AnnaMariaIsland.plotB <-
 ggplot(AnnaMariaIsland, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2003-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMariaIsland.plotB


plot_grid(AnnaMariaIsland.plotA, AnnaMariaIsland.plotB, nrow=1, align='h')



#Destin
Destin <- Radiance_data_long_filtered %>% 
  filter(County == "Destin")

Destin.plotA <-
 ggplot(Destin, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Destin", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2004-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

Destin.plotA


Destin.plotB <-
 ggplot(Destin, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Destin", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2004-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

Destin.plotB


plot_grid(Destin.plotA, Destin.plotB, nrow=1, align='h')




#Pinelals County
PinelalsCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Pinelals County")

PinelalsCounty.plotA <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Pinelals County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2004-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotA


PinelalsCounty.plotB <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Pinelals County", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2004-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotB


plot_grid(PinelalsCounty.plotA, PinelalsCounty.plotB, nrow=1, align='h')



#Santa Rosa
SantaRosa <- Radiance_data_long_filtered %>% 
  filter(County == "Santa Rosa")

SantaRosa.plotA <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Santa Rosa", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2005-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotA


SantaRosa.plotB <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Santa Rosa", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2005-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotB


plot_grid(SantaRosa.plotA, SantaRosa.plotB, nrow=1, align='h')
```



## Time Series 


**Locations with increasing radiance trend before and after policy**



```{r warning=FALSE, message=FALSE, include = FALSE}

#Bay County
BayCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Bay County")

BayCounty.plotA <-
 ggplot(BayCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Bay County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2002-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BayCounty.plotA


BayCounty.plotB <-
 ggplot(BayCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y=" ")+
  ggtitle(" ", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2002-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BayCounty.plotB
```

```{r warning=FALSE, message=FALSE, echo=FALSE}
plot_grid(BayCounty.plotA, BayCounty.plotB, nrow=1, align='h')

```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Mexico Beach
MexicoBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Meixco Beach")

MexicoBeach.plotA <-
 ggplot(MexicoBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Mexico Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

MexicoBeach.plotA



MexicoBeach.plotB <-
 ggplot(MexicoBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

MexicoBeach.plotB

```

```{r warning=FALSE, message=FALSE, echo=FALSE}
plot_grid(MexicoBeach.plotA, MexicoBeach.plotB, nrow=1, align='h')

```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Santa Rosa
SantaRosa <- Radiance_data_long_filtered %>% 
  filter(County == "Santa Rosa")

SantaRosa.plotA <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Santa Rosa", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2005-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotA


SantaRosa.plotB <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2005-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotB

```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(SantaRosa.plotA, SantaRosa.plotB, nrow=1, align='h')

```



**Locations with decreasing radiance trends before and after policy**

```{r warning=FALSE, message=FALSE, include = FALSE}
#Gulf County
GulfCounty <- Radiance_data_long_filtered %>% 
  filter(County == "GUlf COunty")

GulfCounty.plotA <-
 ggplot(GulfCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Gulf County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

GulfCounty.plotA



GulfCounty.plotB <-
 ggplot(GulfCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

GulfCounty.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(GulfCounty.plotA, GulfCounty.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Pinelals County
PinelalsCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Pinelals County")

PinelalsCounty.plotA <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Pinelals County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2004-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotA


PinelalsCounty.plotB <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2004-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(PinelalsCounty.plotA, PinelalsCounty.plotB, nrow=1, align='h')

```


**Locations decreasing before policy and increasing after policy**

```{r warning=FALSE, message=FALSE, include = FALSE}
#Deerfield Beach
DeerfieldBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Deerfield Beach")

DeerfieldBeach.plotA <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Deerfield Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2000-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

DeerfieldBeach.plotA


DeerfieldBeach.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2000-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

DeerfieldBeach.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(DeerfieldBeach.plotA, DeerfieldBeach.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Fort Lauderdale
FortLauderdale <- Radiance_data_long_filtered %>% 
  filter(County == "Fort Lauderdale")

FortLauderdale.plotA <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Fort Lauderdale", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2003-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FortLauderdale.plotA



FortLauderdale.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2003-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FortLauderdale.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(FortLauderdale.plotA, FortLauderdale.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Hallandale Beach
HallandaleBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Hallandale Beach")

HallandaleBeach.plotA <-
 ggplot(HallandaleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Hallandale Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

HallandaleBeach.plotA



HallandaleBeach.plotB <-
 ggplot(DeerfieldBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

HallandaleBeach.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(HallandaleBeach.plotA, HallandaleBeach.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Lauderdale By the Sea
LauderdaleBySea <- Radiance_data_long_filtered %>% 
  filter(County == "Lauderdale By the Sea")

LauderdaleBySea.plotA <-
 ggplot(LauderdaleBySea, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Lauderdale By the Sea", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2002-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

LauderdaleBySea.plotA


LauderdaleBySea.plotB <-
 ggplot(LauderdaleBySea, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2002-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2002-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

LauderdaleBySea.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(LauderdaleBySea.plotA, LauderdaleBySea.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Jacksonville Beach
JacksonvilleBeach <- Radiance_data_long_filtered %>% 
  filter(County == "Jacksonville beach")

JacksonvilleBeach.plotA <-
 ggplot(JacksonvilleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Jacksonville Beach", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2000-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

JacksonvilleBeach.plotA



JacksonvilleBeach.plotB <-
 ggplot(JacksonvilleBeach, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2000-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2000-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

JacksonvilleBeach.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(JacksonvilleBeach.plotA, JacksonvilleBeach.plotB, nrow=1, align='h')
```


```{r warning=FALSE, message=FALSE, include = FALSE}
#Flagler County
FlaglerCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Flagler COunty")

FlaglerCounty.plotA <-
 ggplot(FlaglerCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Flagler County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FlaglerCounty.plotA



FlaglerCounty.plotB <-
 ggplot(FlaglerCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

FlaglerCounty.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(FlaglerCounty.plotA, FlaglerCounty.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Bonita Springs
BonitaSprings <- Radiance_data_long_filtered %>% 
  filter(County == "Bonita SPrings")

BonitaSprings.plotA <-
 ggplot(BonitaSprings, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Bonita Springs", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2001-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BonitaSprings.plotA


BonitaSprings.plotB <-
 ggplot(BonitaSprings, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2001-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2001-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

BonitaSprings.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(BonitaSprings.plotA, BonitaSprings.plotB, nrow=1, align='h')
```

```{r warning=FALSE, message=FALSE, include = FALSE}
#Anna Maria Island
AnnaMariaIsland <- Radiance_data_long_filtered %>% 
  filter(County == "Anna Maria Island")

AnnaMariaIsland.plotA <-
 ggplot(AnnaMariaIsland, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Anna Maria Island", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2003-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMariaIsland.plotA


AnnaMariaIsland.plotB <-
 ggplot(AnnaMariaIsland, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2003-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2003-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

AnnaMariaIsland.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(AnnaMariaIsland.plotA, AnnaMariaIsland.plotB, nrow=1, align='h')
```


```{r warning=FALSE, message=FALSE, include = FALSE}
#Destin
Destin <- Radiance_data_long_filtered %>% 
  filter(County == "Destin")

Destin.plotA <-
 ggplot(Destin, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Destin", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2004-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

Destin.plotA


Destin.plotB <-
 ggplot(Destin, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="")+
  ggtitle("", subtitle= "After policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2004-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

Destin.plotB
```

```{r warning=FALSE, message=FALSE, echo = FALSE}
plot_grid(Destin.plotA, Destin.plotB, nrow=1, align='h')
```


```

**Locations with no obvious differences before and after policy (whether increasing or decreasing trends)**

```{r eval= FALSE, include = FALSE, warning=FALSE, message=FALSE}
#Santa Rosa
SantaRosa <- Radiance_data_long_filtered %>% 
  filter(County == "Santa Rosa")

SantaRosa.plotA <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Santa Rosa", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2005-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotA


SantaRosa.plotB <-
 ggplot(SantaRosa, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Santa Rosa", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2005-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2005-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

SantaRosa.plotB


plot_grid(SantaRosa.plotA, SantaRosa.plotB, nrow=1, align='h')



#Pinelals County
PinelalsCounty <- Radiance_data_long_filtered %>% 
  filter(County == "Pinelals County")

PinelalsCounty.plotA <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Pinelals County", subtitle= "Average annual radiance before policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("1992-01-01","2004-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotA


PinelalsCounty.plotB <-
 ggplot(PinelalsCounty, aes (x=Date, y=value))+
  geom_line()+
  labs(x="Year", y="Radiance")+
  ggtitle("Pinelals County", subtitle= "Average annual radiance after policy")+
  geom_vline(xintercept = as.numeric(ymd("2004-01-01")), lty=2, color ="red")+
  theme(plot.title=element_text(hjust=0.5, face="bold"), plot.subtitle = element_text(hjust=0.5))+
  theme(axis.text.x = element_text(angle=45, hjust=1))+
  scale_x_date(limits=as.Date(c("2004-01-01", "2013-01-01")), date_breaks = "2 years", date_labels = "%Y")+
  geom_smooth(method = "lm", se = FALSE)

PinelalsCounty.plotB


plot_grid(PinelalsCounty.plotA, PinelalsCounty.plotB, nrow=1, align='h')
```

**Results Summary**
* 

**Analysis**


